Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-04 thesis/paper.tex
Changed folder structure, removed unwanted course folders and made changes to the paper.

@@

\subsection{RQ1 Results}
%This should probably go in Methodology... parts of it at least /W
Each change between versions has been identified and grouped into four particular categories reflecting what kind of change they were; New, Modified, Removed and General Trends. Each section introduces the change and then discusses what the changes entailed, how we perceived them in relation to the twelve maintenance types, what our interviewee said about the changes and finally how the interviewees views of the changes relate to the maintenance categories. Each change was given a main category of maintenance and a subcategory if appropriate. This information will be used to answer \textbf{RQ1} and \textbf{RQ1.1}.

@@

@@

We concluded that this change was enhancive as it is a brand-new feature of the API. No sub categories were found to be suitable.

@@

%%Explain how this relates to the category
Based on the interviewees comments, we concluded that we had correctly identified the change as being enhancive. Furthermore, we were also correct in our assumption that there were no suitable subcategories as there was no additional insight into other motivations for the inclusion of this feature.

@@

%%Relate it to Categories
This change was also determined to be enhancive as it was an inclusion of a brand-new feature to the API. Similarly to the axptz, there were no suitable sub categories that could be found to apply to this change.

@@

%%Category based on her information
Based on the information available, we concluded that we had successfully determined that the change was enhancive. Once more, there was no supporting evidence to suggest any suitable subcategories for this change.

@@

Enhancive was once again chosen to be the most applicable category of change given that axstorage was a brand-new inclusion in the newest version of the API. Similarly, there were no appropriate subcategories for this change.

@@

%%Relate it to Categories
The inclusion of this new feature was once again determined to be an enhancive change as it involved the addition of a brand new feature. No relevant subcategories were found.

@@

%%Real category
Given this information, we concluded that we were correct in deciding that this change was also enhancive. Again, we were also correct in the assumption that there were no suitable subcategories for this change.

@@

Given this information we can safely say that we correctly concluded that this was a reductive maintenance task and that there are indeed no other subcategories which are applicable to describe this change.

@@

We therefore gave this change the main categorisation of adaptive with no suitable subcategories being found.

@@

Overwhelmingly, the primary driving factor behind API evolution appears to have been the desire for new API functionality. We found strong evidence to suggest that most, if not all of the additions, re-implementations and functional changes were undertaken to include functionality that the partners desired. Specifically we found that 53.8\% of the changes were enhancive changes, 7.7\% were adaptive and the remaining 38.5\% were changes specifically aimed at improving the maintainability of the API.

@@

@@

Interesting that the majority of the changes seem to be driven either by management (Suggested that it comes from partners) or the partners directly. There was also internal pressure to improve the API which came about from Axis developers trying to create their own applications.

>>>>

%This should probably go in Methodology... parts of it at least /W
Each change between versions has been identified and grouped into four particular categories reflecting what kind of change they were; New, Modified, Removed and General Trends. Each section introduces the change and then discusses what the changes entailed, how we perceived them in relation to the twelve maintenance types, what our interviewee said about the changes and finally how the interviewees views of the changes relate to the maintenance categories. Each change was given a main category of maintenance and a subcategory if appropriate. This information will be used to answer \textbf{RQ1} and \textbf{RQ1.1}.

@@

%%Intoduce the four sections added, removed, modified & general trends.

\subsection{RQ1 Results}

%% Check what willy wrote.
%%Explain structure of this section around the RQ and a summary of it. Table with the percentages from both us and her.

Specifically we found that 53.8\% of the changes were enhancive changes, 7.7\% were adaptive and the remaining 38.5\% were changes specifically aimed at improving the maintainability of the API.

@@

%Discuss how there were many modifications but we've classified them as re-implementations. Includes a deprecation and a replacement of that deprecation. Alternative was to analyse modify them as both an addition and a deprecation.

@@

We concluded that this change was enhancive as it is a brand-new feature of the API. No sub-categories were found to be suitable.

@@

%%Explain how this relates to the category
Based on the interviewees comments, we concluded that we had correctly identified the change as being enhancive. Furthermore, we were also correct in our assumption that there were no suitable sub-categories as there was no additional insight into other motivations for the inclusion of this feature.

@@

%%Relate it to Categories
This change was also determined to be enhancive as it was an inclusion of a brand-new feature to the API. Similarly to the axptz, there were no suitable sub-categories that could be found to apply to this change.

@@

%%Category based on her information
Based on the information available, we concluded that we had successfully determined that the change was enhancive. Once more, there was no supporting evidence to suggest any suitable sub-categories for this change.

@@

Enhancive was once again chosen to be the most applicable category of change given that axstorage was a brand-new inclusion in the newest version of the API. Similarly, there were no appropriate sub-categories for this change.

@@

%%Relate it to Categories
The inclusion of this new feature was once again determined to be an enhancive change as it involved the addition of a brand new feature. No relevant sub-categories were found.

@@

%%Real category
Given this information, we concluded that we were correct in deciding that this change was also enhancive. Again, we were also correct in the assumption that there were no suitable sub-categories for this change.

@@

Given this information we can safely say that we correctly concluded that this was a reductive maintenance task and that there are indeed no other sub-categories which are applicable to describe this change.

@@

We therefore gave this change the main categorisation of adaptive with no suitable sub-categories being found.

@@

Overwhelmingly, the primary driving factor behind API evolution appears to have been the desire for new API functionality. We found strong evidence to suggest that most, if not all of the additions, re-implementations and functional changes were undertaken to include functionality that the partners desired.

@@

% 1 - Desire for new functionality
% 2 - Push for new functionality from partners
% 3 - Desire for a well designed API, interface improvements
% 4 - Desire to have a more maintainable API
%

@@
